Estimating Operator Intent\\ (Draft 2.1)

### 2015-09-25 design-goals.tex
cga updates

Can we build an exoskeleton allows the operator to behave naturally
and exerts little or no force on the operator?

@@

Can we build an exoskeleton allows the operator to behave naturally?
The operator can feel the exoskeleton, but can overpower it when necessary.

>>>>

Can we build an exoskeleton that allows the operator to behave naturally
and exerts little or no force on the operator?

@@

Can we build an exoskeleton that allows the operator to behave naturally?
The operator can feel the exoskeleton, but can overpower it when necessary.
